Concurrent Programming in Harmony

### 2021-12-26 book/paper.tex
Added a practical note

>>>>

The model has each replica send its entire history each time it extends
its history.  This is fine for modeling, but in practice that would not
scale.  In practice, a predecessor would set up a TCP connection to
its successor and only send updates to its history along the TCP
connection.  Because TCP connections guarantee FIFO order, this would
be identical to the predecessor sending a series of histories, but
much more efficient.
